WASP-4\lowercase{b} Arrived Early for the TESS Mission

### 2018-12-14 paper/ms.tex
grammar-hammer

The middle panel of Figure~\ref{fig:context} shows the expected
orbital decay time of WASP-4b compared to other transiting giant
planets.  Although roughly 20 hot Jupiters have shorter predicted
orbital decay times than WASP-4b, most have short observing baselines.
A separate consideration is that some hot Jupiters host stars ({\it
e.g.}, WASP-18) are fully radiative, and may dissipate tidal energy
less efficiently than stars with convective zones, like WASP-4.

>>>>

The middle panel of Figure~\ref{fig:context} shows the expected
orbital decay time of WASP-4b compared to other transiting giant
planets.  Although roughly 20 hot Jupiters have shorter predicted
orbital decay times than WASP-4b, most have shorter observing
baselines.  A separate consideration is that some hot Jupiter host
stars ({\it e.g.}, WASP-18) are fully radiative, and may dissipate
tidal energy less efficiently than stars with convective zones, like
WASP-4.
